Transferability of clinical prediction models for early trauma care

### 2019-06-04 ManuscriptMarkdown.Rmd
Add files via upload

---
title: "Transferability of clinical prediction models for early trauma care"
author: 
- Martin Gerdin Wärnberg
- Martin Henriksson
- Johanna Berg
- Dell Saulnier
date: "June 04, 2019"
documentclass: "article"
output: html_document
header-includes:
   - \usepackage{hyperref}
bibliography: library.bib
csl: bmcemerg.csl
---
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
## LOAD FUNCTIONS, ENVIROMENT AND TABLES
  ## Source functions
  source("functions/WorkTableCreator.R")
  ## Original results
  results <- readRDS("output/original.results.Rds")
  ## Compiled results with UI
  result.tables <- readRDS("result.tables.Rds")
  ## Compiled results with UI as data frame
  result.tables.data.frame <- readRDS("result.tables.data.frame.Rds")
  ## Create table for ease of data retrival
  results.all.data <- WorkTableCreator(result.tables.data.frame)
  ## Sample characteristics table
  # table.one <-

@@

**Table 1. Sample characteristics of multiple imputed data.** Data is presented as medians with interquartile range (IQR) or counts with % as applicable.
```{r, echo = FALSE, results = "asis"} 
## Table 1 = Sample characteristics table
##result.tables
```

>>>>

title: "Transferability of clinical prediction models for early trauma care"
author: 
- Martin Gerdin Wärnberg
- Martin Henriksson
- Johanna Berg
- Dell Saulnier
date: "June 04, 2019"
documentclass: "article"
output: html_document
header-includes:
   - \usepackage{hyperref}
bibliography: library.bib
csl: bmcemerg.csl
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
## LOAD FUNCTIONS, ENVIROMENT AND TABLES
  ## Source functions
  source("functions/WorkTableCreator.R")
  ## Original results
  results <- readRDS("output/original.results.Rds")
  ## Compiled results with UI
  result.tables <- readRDS("result.tables.Rds")
  ## Compiled results with UI as data frame
  result.tables.data.frame <- readRDS("result.tables.data.frame.Rds")
  ## Create table for ease of data retrival
  results.all.data <- WorkTableCreator(result.tables.data.frame)
  ## Sample characteristics table  (Retrived locally!)
  library(readxl)
  table_one_high_low <- read_excel("table one/table one high low.xlsx")
  table_one_metro_non_metro <- read_excel("table one/table one metro non metro.xlsx")
  table_one_multi_single <- read_excel("table one/table one multi single.xlsx")

@@

**Table 1. Sample characteristics of multiple imputed data.** Data is presented as medians with interquartile range (IQR) or counts with % as applicable.
```{r, echo = FALSE, results = "asis"} 
## Table 1
options(knitr.kable.NA = '')
kable(table_one_high_low, format = "markdown")
kable(table_one_metro_non_metro, format = "markdown")
kable(table_one_multi_single, format = "markdown")
``` 
Abbreviations: GCS glasgow coma scale, SBP systolic blood pressure, RR respiratory rate, ISS injury severity score, NISS new injury severity score
